Regular singular Volterra equations on complex domains

### 2023-08-16 reg-sing-volterra.tex
Revise prop:alt-general_volterra and associated remarks

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:asymptotics}.

\begin{rmk}
Under stronger conditions on $p$, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics} for details.

%%Suppose $p$ falls into the class $B\zeta + O\big(|\zeta|^2\big)$, for some constant $B$, when it's restricted to some neighborhood of $\zeta = 0$.

%%for some constant $B$, we can strengthen the conclusion of Theorem~\ref{thm:proto-growth}. Under {\em Condition~\eqref{cond:sing}}, we can show that $\solproto \in B\zeta^{\tau-1} + O(|\zeta|^\tau)$.

%%If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant multiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.
\end{rmk}
\color{black}

@@

\begin{rmk}
Under stronger conditions on $p$, Theorem~\ref{thm:general_volterra} can be restated to provide a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \singexpalg{\tau-1+\gamma}(\Omega). \]
as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
\end{rmk}
%%To prove Theorem~\ref{thm:general_volterra}, we will rewrite the homogeneous equation we want to solve as an inhomogeneous one, with $\softpart f_0$ as the inhomogeneous term.

@@

\begin{prop}\label{prop:alt-general_volterra}
    Suppose $p$ satisfies Condition \eqref{cond:reg-p}, and $\volterra$ satisfies the assumptions of Theorem \ref{thm:general_volterra}. Then equation 
    \[f=\volterra f\]
    has a unique solution $f$ in the affine subspace
    \[ M \zeta^{\tau-1}+\singexpalg{\tau-1+\gamma'}(\domain)\]
    of the space $\singexpalg{\tau-1}(\domain)$, where $\gamma'=\min\{\epsilon, 1, \gamma\}$. 
\end{prop}

\begin{proof}
 By Theorem \ref{thm:general_volterra}, we already know there exists a unique solution $f$ which belongs to the affine subspace
 \[f_0+\singexpalg{\tau+1-\gamma}(\domain)\]
 of the space $\singexpalg{\tau-1}(\domain)$. In addition, in Proposition \ref{prop:better-proto-estimate}, we learnt that in a neighbourhood of $\zeta=0$
 \[\solproto\in M\zeta^{\tau-1}+ O(|\zeta|^{\tau-1+\lambda'})\]
 for some constant $M$ and $\lambda'=\min\{\epsilon, 1\}$. We conclude, by combining these results. 
\end{proof}

>>>>

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:asymptotics}.
\begin{rmk}
When $\hardpart$ also satisfies Condition~\eqref{cond:reg-p}, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics}.
\end{rmk}
\color{black}

@@

\begin{rmk}
When $\hardpart$ also satisfies Condition~\eqref{cond:reg-p}, Theorem~\ref{thm:general_volterra} can be restated to give a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) \]
when $\rho > \tau$ is low enough, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
\end{rmk}
%%To prove Theorem~\ref{thm:general_volterra}, we will rewrite the homogeneous equation we want to solve as an inhomogeneous one, with $\softpart f_0$ as the inhomogeneous term.

@@

\begin{prop}\label{prop:alt-general_volterra}
Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other conditions we assume in {\em Theorem~\ref{thm:general_volterra}}. Then, as long as $\rho > \tau$ is low enough, the equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
of the space $\singexpalg{\tau-1}(\domain)$. To be precise, $\rho$ is low enough when it's in the interval
\[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]
\end{prop}

\begin{proof}
Proposition~\ref{prop:better-proto-estimate} implies that for some constant $M$,
\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
whenever $\rho \le \tau + \min\{\epsilon, 1\}$. Theorem~\ref{thm:general_volterra} implies that our equation has a unique solution in
\[ M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
as long as $\rho \in (\tau, \tau + \gamma]$. Putting these facts together, we get the desired result.
\end{proof}
